When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-02-23 presentation/inbreeding.Rmd
Working nice figure of allele change

```{r lmSim, fig.show='animate', echo = FALSE}
inputPanel(
  sliderInput("Imm", label = "Immigrants", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  sliderInput("ID", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  sliderInput("cost", label = "Strategy Cost", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  sliderInput("mu", label = "Mutation Rate", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  actionButton("mate", "New Generation"),
  actionButton("reset", "Reset")
)

gen     <- reactiveValues();

gen$dat <- list(ID = NULL, Rmat = NULL);

Ds    <- observeEvent(input$mate, {

        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
            gen$dat$ID   <- initialise_inds(N = 8);
            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
        }else{
            gen$dat <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
                               Kf = 40, Km = 40, beta = 8, imm = 1);
        }
})

rs    <- observeEvent(input$reset, {
       gen$dat <- list(ID = NULL, Rmat = NULL);
})

renderPlot({
  par(bg = 'transparent');
  kval <- gen$dat$Rmat;
  kval <- as.matrix(kval);
  kval <- kval[,-1];
  diag(kval) <- diag(kval)/2;
  hist(kval);
  #size <- hist(gen$dat$ID)[1];
  #if(5 < 6){
  #    plot(x = 0:10, y = 0:10, type = "n", ylim = c(0, 400), cex.axis = 1.5,
  #         cex.lab = 1.5, xlab = "Generation", ylab = "k", bg = "transparent");
  #    points(x = 2, y = size, pch = 20, cex = 1.5, type = "b",
  #           lwd = 2);
  #}#else{
#      x0 <- last - 5;
#      x1 <- last + 5;
#      plot(x = x0:x1, y = x0:x1, type = "n", ylim = c(0, 1), cex.axis = 1.5,
#           cex.lab = 1.5, xlab = "Generation", ylab = "k");
#      points(x = ts$df[x0:x1,1], y = ts$df[x0:x1,2], pch = 20, cex = 1.5, type = "b",
#             lwd = 2);
#  }
})
```

>>>>

```{r lmSim, fig.show='animate', echo = FALSE}
inputPanel(
  sliderInput("Imm", label = "Immigrants", width="100%",
              min = 0.0, max = 10, value = 0, step = 1), 
  sliderInput("ID", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 10, value = 0, step = 0.5), 
  sliderInput("cost", label = "Strategy Cost", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  sliderInput("mu", label = "Mutation Rate", width="100%",
              min = 0.0, max = 0.1, value = 0, step = 0.01), 
  actionButton("mate", "New Generation"),
  actionButton("reset", "Reset")
)

gen     <- reactiveValues();
iter    <- reactiveValues();

gen$dat  <- list(ID = NULL, Rmat = NULL);
iter$all <- 0;
iter$nue <- 0;

Ds    <- observeEvent(input$mate, {
        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
            gen$dat$ID   <- initialise_inds(N = 8);
            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
        }else{
            gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
                                Kf = 40, Km = 40, beta = input$ID, 
                                imm = input$Imm, cost = input$cost, 
                                mu = input$mu);
            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
        }
})

rs    <- observeEvent(input$reset, {
       gen$dat <- list(ID = NULL, Rmat = NULL);
       iter$all <- 0;
       iter$nue <- 0;
})

renderPlot({
  par(bg = 'transparent');
  malle <- iter$all;
  mneut <- iter$nue
  gens  <- 1:length(iter$all);
  if(length(gens) < 6){
      plot(x = 0:10, y = 0:10, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
           cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
           bg = "transparent");
      abline(h = 0, lty = "dotted", lwd = 0.8);
      polygon(x=c(-0.125, 2.5, 2.5, -0.125), y=c(0.825, 0.825, 1.1, 1.1), 
              border=NA, col="black");
      polygon(x=c(-0.125, 2.5, 2.5, -0.125), y=c(-0.825, -0.825, -1.1, -1.1), 
              border=NA, col="black");
      abline(v = -0.125, lwd = 4);
      text(x = 0, y = 0.95, labels = "Inbreeding Preference", cex = 1.5, 
           col = "white", pos = 4);
      text(x = 0, y = -0.95, labels = "Inbreeding Avoidance", cex = 1.5, 
           col = "white", pos = 4);
      if(length(gens) > 0){
          points(x = gens, y = malle, pch = 20, cex = 1.5, type = "b",
                 lwd = 2, col = "black");
      }
  }else{
      x0 <- length(gens) - 5;
      x1 <- length(gens) + 5;
      plot(x = x0:x1, y = 0:10, type = "n", ylim = c(-1, 1), cex.axis = 1.5,
           cex.lab = 1.5, xlab = "Generation", ylab = "Inbreeding strategy", 
           bg = "transparent");
      abline(h = 0, lty = "dotted", lwd = 0.8);
      polygon(x=c(x0-0.125, x0+2.5, x0+2.5, x0-0.125), 
              y=c(0.825, 0.825, 1.1, 1.1), border=NA, col="black");
      polygon(x=c(x0-0.125, x0+2.5, x0+2.5, x0-0.125), 
              y=c(-0.825, -0.825, -1.1, -1.1), border=NA, col="black");
      abline(v = x0-0.125, lwd = 4);
      text(x = x0, y = 0.95, labels = "Inbreeding Preference", cex = 1.5, 
           col = "white", pos = 4);
      text(x = x0, y = -0.95, labels = "Inbreeding Avoidance", cex = 1.5, 
           col = "white", pos = 4);
      points(x = gens, y = malle, pch = 20, cex = 1.5, type = "b",
                 lwd = 2, col = "black");
  }
})
```
